A Comparison of Algorithms Playing EvoMan

### 2020-07-05 paper/paper.tex
Corrected table with results.
Added average.
Report updated for specialized PPO.

    \begin{table}[htbp]
        \caption{Average player and enemy life. Average game duration}
        \begin{center}
            \begin{tabular}{|c|c|c|c|c|c|c|}
                \hline
                \textbf{Opponent}&\multicolumn{3}{|c|}{\textbf{Best train agent}}&\multicolumn{3}{|c|}{\textbf{Best test agent}} \\
                \cline{2-7}
                & \textbf{\textit{Avg player life}}& \textbf{\textit{Avg enemy life}}& \textbf{\textit{Avg duration}} & \textbf{\textit{Avg player life}}& \textbf{\textit{Avg enemy life}}& \textbf{\textit{Avg duration}} \\
                \hline
                1 & 97.26 &   100 &     0 &     0 & 159.63 & 174.23 \\
                2 & 98.33 & 89.73 &     0 &     0 &  176.6 & 186.43 \\
                3 &  0.13 &  7.66 & 43.33 & 21.33 & 457.26 & 410.53 \\
                4 &     0 &  1.84 & 37.66 & 21.66 &  547.5 & 736.83 \\
                5 & 71.32 & 60.52 &     0 &     0 & 379.13 & 367.93 \\
                6 & 96.32 &    95 &     0 &     0 & 165.06 & 203.53 \\
                7 & 99.74 &  85.9 &     0 &     0 & 162.06 & 135.13 \\
                8 &  34.3 & 38.76 &     6 &     2 & 520.93 & 443.6 \\
                \hline
            \end{tabular}
        \end{center}
    \end{table}

>>>>

    \begin{table}[htbp]
        \caption{Average player and enemy life. Average game duration}
        \begin{center}
            \begin{tabular}{|c|c|c|c|c|c|c|}
                \hline
                \textbf{Opponent}&\multicolumn{3}{|c|}{\textbf{Best train agent}}&\multicolumn{3}{|c|}{\textbf{Best test agent}} \\
                \cline{2-7}
                & \textbf{\textit{Avg player life}}& \textbf{\textit{Avg enemy life}}& \textbf{\textit{Avg duration}} & \textbf{\textit{Avg player life}}& \textbf{\textit{Avg enemy life}}& \textbf{\textit{Avg duration}} \\
                \hline
                1 & 97.26 &     0 &  159.63 &    100 &     0 &  174.23 \\
                2 & 98.33 &     0 &   176.6 &  89.73 &     0 &  186.43 \\
                3 &  0.13 & 43.33 &  457.26 &   7.66 & 21.33 &  410.53 \\
                4 &     0 & 37.66 &   547.5 &   1.84 & 21.66 &  736.83 \\
                5 & 71.32 &     0 &  379.13 &  60.52 &     0 &  367.93 \\
                6 & 96.32 &     0 &  165.06 &     95 &     0 &  203.53 \\
                7 & 99.74 &     0 &  162.06 &   85.9 &     0 &  135.13 \\
                8 &  34.3 &     6 &  520.93 &  38.76 &     2 &   443.6 \\
                \hline
                \textbf{Average} & 62.17 & 10.87 & 321.02 & 59.92 & 5.62 & 332.27 \\
            \end{tabular}
        \end{center}
    \end{table}

    \subsection{Specialized PPO}\label{subsec:specialized-ppo}
    In order to obtain a score higher than the upper bound we have tried two methods:
    \begin{itemize}
        \item A generalized PPO agent trained against all $8$ opponents.
        \item A specialized PPO agent for each of the $8$ opponents.
    \end{itemize}

    \subsubsection{PPO trained against all opponents}
    At the default difficulty of 2, a PPO agent trained against all opponents
    obtained a final gain of 185.57, being lower with 0.1 than the
    upper bound found with specialized NEAT\@.
    For such an agent we have also studied how its gain changes when the difficulty
    is modified.
    \begin{figure}[htbp]
    \centering
    \includegraphics[width=0.5\textwidth]{images/general_harmonic_gain.eps}
    \caption{Gain Evolution for PPO when trained against all 8 opponents.}
    \label{fig:ppo_train_8}
    \end{figure}

    \begin{table}[htbp]
        \caption{PPO trained against all opponents (Gain)}
        \begin{center}
            \begin{tabular}{|c|c|c|c|c|c|}
                \hline
                \textbf{Opponent}&\multicolumn{5}{|c|}{\textbf{Difficulty}} \\
                \cline{2-6}
                & \textbf{\textit{1}}& \textbf{\textit{2}}& \textbf{\textit{3}} & \textbf{\textit{4}} & \textbf{\textit{5}} \\
                \hline
                 1 &  200.01 &  199.54 &  170.75 &  155.48 &   41.08\\
                 2 &  200.01 &  200.01 &  182.81 &  168.81 &  168.51\\
                 3 &  199.38 &  194.81 &  164.31 &  127.54 &  130.61\\
                 4 &  186.14 &  180.61 &  154.23 &  181.58 &   60.28\\
                 5 &  196.56 &  187.77 &  185.34 &  142.41 &  158.31\\
                 6 &  196.35 &  174.43 &  179.19 &   23.84 &    9.88\\
                 7 &  199.26 &  183.07 &   95.40 &    8.01 &    8.28\\
                 8 &  196.57 &  169.31 &  123.00 &   41.34 &   10.01\\
                \hline
                \textbf{harmonic mean} & 196.68 & 185.57 & 149.57 & 35.76 & 20.89 \\
                \hline
            \end{tabular}
            \label{PPO against all opponents gain}
        \end{center}
    \end{table}

    \begin{table}[htbp]
        \caption{PPO trained against all opponents (percent games lost)}
        \begin{center}
            \begin{tabular}{|c|c|c|c|c|c|}
                \hline
                \textbf{Opponent}&\multicolumn{5}{|c|}{\textbf{Difficulty}} \\
                \cline{2-6}
                & \textbf{\textit{1}}& \textbf{\textit{2}}& \textbf{\textit{3}} & \textbf{\textit{4}} & \textbf{\textit{5}} \\
                \hline
                 1 &  0 &  0 &     20 &  23.33 &   100 \\
                 2 &  0 &  0 &      0 &      0 &     0 \\
                 3 &  0 &  0 &      0 &  13.33 &  3.33 \\
                 4 &  0 &  0 &      0 &      0 &    60 \\
                 5 &  0 &  0 &      0 &      0 &     0 \\
                 6 &  0 &  0 &      0 &    100 &   100 \\
                 7 &  0 &  0 &  56.66 &    100 &   100 \\
                 8 &  0 &  0 &     10 &    100 &   100 \\
                \hline
            \end{tabular}
            \label{PPO against all opponents games lost}
        \end{center}
    \end{table}

    \subsubsection{A PPO agent for each opponent}
    In the second attempt to outscore the upper bound we have trained an agent
    for each of the $8$ opponents.
    Due to the high computational time this experiment was done only at
    difficulty 2 and the number of training epochs for PPO was decreased from 3000 to 1000.
    It won all its games against all opponents at difficulty 2.
    \begin{table}[htbp]
        \caption{PPO generalized vs PPO specialized vs NEAT specialized}
        \begin{center}
            \begin{tabular}{|c|c|c|c|}
                \hline
                \textbf{Opponent}&\textbf{PPO g.}&\textbf{PPO s.}&\textbf{NEAT s.} \\
                \hline
                 1 &  199.54 &  199.67 &  190.01 \\
                 2 &  200.01 &  199.61 &  194.01 \\
                 3 &  194.81 &  199.94 &  180.01 \\
                 4 &  180.61 &  195.95 &  194.01 \\
                 5 &  187.77 &  198.03 &  194.01 \\
                 6 &  174.43 &  199.67 &  173.01 \\
                 7 &  183.07 &  197.73 &  177.01 \\
                 8 &  169.31 &  195.07 &  186.01 \\
                \hline
                \textbf{harmonic mean} & 185.57 & 198.19 & 185.67 \\
                \hline
            \end{tabular}
            \label{PPO generalized vs specialized vs NEAT}
        \end{center}
    \end{table}
